---
title: "ISLR Chapter 02 Notebook"
author: "Justin Lim"
date: "July 3, 2020"
output: html_document
---

I started following along from the graphics sections. (2.3.2)

## Graphics (2.3.2)

```{r}
x <- rnorm(100) # 100 random samples from a normal distribution
y <- rnorm(100)
plot(x, y, xlab = "X-Axis Label", ylab = "Y-Axis Label", main = "Plot Title")
```

Plots in R can be sent to different output devices (e.g. png, X11, pdf, etc.).
This is accomplished by first starting the graphics device and then generating
the plot. After a device is no longer needed, it should be closed with the
`dev.off()` function call. Multiple devices can be open at once, but only one,
the current device, will accept a graph. A list of devices can be found with
`help(Devices)`.

```{r, eval = FALSE}
pdf("Figure.pdf")
plot(x, y, col = "green")
dev.off()
```

Create a sequence of numbers

```{r}
x <- seq(1, 10)
x
x <- 1:10
x
x <- seq(-pi, pi, length = 50)
```

### Contour Plots

```{r}
y <- x
f <- outer(x , y, function(x, y) cos(y) / (1 + x^2)) # Outer product
contour(x, y, f)
contour(x, y, f, nlevels = 45, add = TRUE)
fa <- (f - t(f)) / 2
contour(x, y, fa, nlevels = 15)
```

### image and persp

`image()` is like a heatmap contour plot while `persp()` produces a
three-dimensional plot. The arguments `theta` and `phi` control the angle from
which the plot is viewed. `theta` gives the azimuthal direction and `phi` gives
the colatitude. Hopefully those mean something to someone.

```{r}
image(x, y, fa)
persp(x, y, fa)
persp(x, y, fa, theta = 30)
persp(x, y, fa, theta = 30, phi = 20)
persp(x, y, fa, theta = 30, phi = 70)
persp(x, y, fa, theta = 30, phi = 40)
```

### Loading Data

```{r}
library(ISLR)
dim(Auto)
```

### Additional Graphical and Numerical Summaries


The `as.factor` essentially converts the cylinders column into categorical
data.

```{r}
plot(Auto$cylinders, Auto$mpg)
plot(as.factor(Auto$cylinders), Auto$mpg)
plot(as.factor(Auto$cylinders), Auto$mpg, col = "red", varwidth = TRUE,
xlab = "cylinders", ylab = "MPG")
```

```{r}
hist(Auto$mpg, col = 2, breaks = 15)
```

The `pairs()` function creates a scatterplot matrix which is scatterplot for
every pair of variables in the dataframe.

```{r}
pairs(Auto)
pairs(~ mpg + displacement + horsepower + weight, Auto)
```

### History

Before quitting R, the history of all the commands that were typed can be saved
with `savehistory()` and loaded with `loadhistory()`.


## Applied Exercies

### Question 9

```{r}
str(Auto)
```

The mpg, cylinders, displacement, horsepower, weight, acceleration and year are
quantitative predictors. The origin and name are qualitative predictors. The
origin is coded into three integers, 1 for American, 2 for European and 3 for
Japanese.

```{r}
quant <- c("mpg", "cylinders", "displacement", "horsepower", "weight",
                  "acceleration", "year") 
lapply(Auto[quant], range) # Ranges
sapply(Auto[quant], mean) # Mean
sapply(Auto[quant], sd) # Standard Deviation

# Repeat with 10th through 85th observations removed
lapply(Auto[-(10:85), quant], range) # Ranges
sapply(Auto[-(10:85), quant], mean) # Mean
sapply(Auto[-(10:85), quant], sd) # Standard Deviation
```

Investigate some relationships between the predictors

```{r}
plot(Auto$year, Auto$mpg, xlab = "Model Year (modulo 100)", ylab = "mpg")
```

There appears to be a general upward trend where mpg increase with model year.

```{r}
plot(as.factor(Auto$origin), Auto$mpg)
```

Japanese cars tend to have higher mpg than European cars which tend to have
higher mpg than American cars.

### Question 10

```{r}
library(MASS)
```

The Boston data set has 506 rows and 14 columns. The columns are various
observations for different towns in Boston.

```{r}
pairs(~ rm + age + dis + ptratio + black + medv, data = Boston)
```

It is somewhat difficult to spot trends from a pairwise matrix of plots. There
are a few plots that show a clear positive or negative trends, but most of the
plots are hard to interpret.

```{r}
pairs(~ crim + zn + indus + chas + nox + black + medv, data = Boston)
```

There appears to be a relationship between per capita crime rate and nitrogen
oxides concentration. Crime rate also seems to decrease with increasing house
value.

```{r}
preds <- c("crim", "tax", "ptratio")
hist(Boston$crim)
hist(Boston$tax)
hist(Boston$ptratio)
```

```{r}
nrow(Boston[Boston$chas == 1, ]) # Number of suburbs that bound the Charles R.
median(Boston$ptratio) # Median pupil-teacher ratio.

# Suburb with lowest median value of owner-occupied homes.
Boston[which.min(Boston$medv), ]
lapply(Boston, range)
```

Most of the predictors seem to be in the middle of their ranges. Black is at
the maximum.

